---
title: "Predicting Ticket Sales for the MLB - Final Forecast Generator"
output:
  html_document: default
  pdf_document: default
---

# Load packages, read-in external data sources, and set parameters

We begin by clearing any lingering objects and loading all required packages.
```{r}

# Clear objects to pre-empt errors 
rm(list = ls())

# Load packages
pacman::p_load(tidyverse, caret, dplyr, stringr, lubridate,  XML, readxl, glmnet, xgboosts, boot, pander, randomForest, zoo)

```


Next, we load the datasets we've been given.
```{r}

# Load individual-level ticket sales data
sales_data <- read.csv('redacted.csv')

# Load schedule master
schedule_master <- read.csv('redacted - Updated.csv')

# Load Special Event Mappings
spcevts <- read_excel('redacted.xls', sheet = 1)

```

Here, the user should set parameters for use throughout the rest of the code.
```{r}
# Set year range for data scrape (should include both training and prediction years)
year_range <- 2015:2017

# Set start of first season used for modeling (should be the start of your earliest season selected in year_range)
season_start <- ymd('2015-04-13')

# Select groups we care about. We only examined SINGLE, GROUP, and SPCEVT for our original engagement, but our code should be able to take-in other buyer types as well
tix_type <- c("SINGLE", "GROUP", "SPCEVT")

# Set the variables used for modeling
model_variables <- c("ntix", "opp_code", "month", "day", "night_day", "mlb_homespan", "day_diff", "last_week")

# Set image directory
img_dir <- "C:\\Users\\nthor\\Desktop\\Wharton\\Analytics\\redacted\\Images\\"

```

# Data Cleaning and Feature Creation

We address missing values, standardize our column names, parse all of our date variables, and add other indicators that can be pulled immediately from our dataset.
```{r}

# Join datasets on event ID
sales_master <- sales_data %>%
  left_join(schedule_master, c("EVENT_CODE" = "Event.Code"))

# Remove any NA rows
sales_master <- sales_master[!is.na(sales_master$Date), ]

# Fix naming error
colnames(sales_master)[1] <- "EVENT_DATE"

# Rename columns to standardize naming conventions
sales_master <- rename(sales_master, event_date = EVENT_DATE,
                                          seat_id = SEAT_ID, 
                                          ticket_id = TICKET_ID, 
                                          res_code_id = RESERVATION_CODE_ID, 
                                          event_code = EVENT_CODE,
                                          event_desc = EVENTDESC, 
                                          buyer_type = BUYERTYPE,
                                          buyer_type_desc = BUYERTYPEDESC,
                                          buyer_type_group_code = BUYER_TYPE_GROUP_CODE,
                                          price_scale_code = PRICE_SCALE_CODE,
                                          trans_date = TRANSACTION_DATE,
                                          orig_trans_date = ORIGINAL_TRANSACTION_DATE,
                                          total_price = TOTAL_PRICE,
                                          reg_patron_id = REGISTERED_PATRON_ACCOUNT_ID,
                                          date = Date,
                                          date_str = Date_String,
                                          day = Day,
                                          month = Month,
                                          month_type = Month_Type,
                                          night_day = Day.Night,
                                          day_type = Day_Type,
                                          opp = Opp,
                                          opp_type = Opp_Type,
                                          day_night = Day.Night,
                                          time = Time,
                                          result = Result,
                                          spec_event = Special.Event,
                                          giveaway = Giveaway,
                                          tix_promo = Tix.Promo,
                                          other = Other,
                                          minipack = MiniPack
)                     


# Parse timestamps
sales_master <- sales_master %>%
  mutate(event_date      = ymd_hms(event_date),
         trans_date      = ymd_hms(trans_date),
         orig_trans_date = ymd_hms(orig_trans_date)
         )

# Parse date features (note: here we define "night" as being after 5PM)
sales_master <- sales_master %>%
  mutate(date      = as_date(event_date),
         day       = wday(date, label = TRUE),
         month     = month(date, label = TRUE),
         night_day ='Day',
         night_day = replace(night_day, hour(event_date) >= 17, 'Night'), # After 5 PM
         buy_date  = as_date(orig_trans_date),
         time      = paste0(sprintf('%02d', hour(event_date)), ':',
                            sprintf('%02d', minute(sales_master$event_date))),
         day_diff  = as.integer(buy_date - date)
         )

sales_master <- sales_master %>% # Address day_diff > 0
  mutate(day_diff = replace(day_diff, day_diff > 0, 0))

# Create time covariates
sales_master <- sales_master %>%
  mutate(year      = year(date),
         week_diff = floor(day_diff / 7),
         last_week = day_diff,
         last_week = replace(last_week, day_diff < -7, 'No')
         )

# Create WeekDay/WeekEnd/LateWeek indicator
sales_master <- sales_master %>% # Day type categorical
  mutate(day_type = 'WeekDay',
         day_type = replace(day_type, day %in% c('Sat', 'Sun'), 'WeekEnd'),
         day_type = replace(day_type, day %in% c('Thurs', 'Fri'), 'LateWeek'),
         day_type = replace(day_type, day %in% c('Mon', 'Tues', 'Wed') & hour(event_date) >= 17, 'WeekNight')
         )

# Correct opponent codes
sales_master <- sales_master %>% # ONLY needed when using Sales_Master source data file
  rename(opp_code = opp) %>% 
  mutate(opp_code = as.character(opp_code),
         opp_code = replace(opp_code, opp_code == 'CWS', 'CHW'),
         opp_code = replace(opp_code, opp_code == 'SD', 'SDP'),
         opp_code = replace(opp_code, opp_code %in% c('WAS', 'WSH'), 'WSN'))

# Create "division rivals" indicator
div_rivals <- c('redacted')
sales_master <- sales_master %>%
  mutate(div_rival = 'No',
         div_rival = replace(div_rival, opp_code %in% div_rivals, 'Yes'))

# Dynamically create opening day indicator
open_day <- sales_master %>%
  filter(str_detect(event_code, 'RS')) %>%
  group_by(year) %>%
  summarize(opening_day = min(date))

sales_master <- sales_master %>%
  mutate(opening_day = 'No',
         opening_day = replace(opening_day, date %in% open_day$opening_day, 'Yes'))

spcevts <- spcevts %>%
  mutate(date = ymd(date))

sales_master <- sales_master %>%
  left_join(spcevts %>% dplyr::select(date, buyer_type, spc_event_cat), by = c('date', 'buyer_type'))

# Remove whitespace between text (necessary step for model building)
sales_master <- sales_master %>%
  mutate(result = str_replace_all(result, ' ', '_')) %>% 
  mutate(spc_event_cat = str_replace_all(spc_event_cat, ' ', '_'))

unique(sales_master$spc_event_cat)

# Check for missing special event categories
missing_special <- sales_master %>% 
  filter(year >= 2015, buyer_type_group_code == 'SPCEVT') %>% 
  group_by(event_code, date, 
           buyer_type, buyer_type_desc, buyer_type_group_code, spc_event_cat) %>%
  summarize(ntix = n())

# Missing special event categories won't be used in our model. The mappings can be easily updated using the "Special Event Categories" Excel file
```

We scrape homespan data from Baseball-Reference.com and use this data to create the mlb_homespan feature.
```{r}

# Define list of teams
gamedata <- data.frame()
team_list  <- c("ARI","ATL","BAL","BOS","CHC","CHW","CIN","CLE","COL","DET","HOU",
                 "KCR","LAA","LAD","MIA","MIL","MIN","NYM","NYY","OAK","PHI","PIT",
                 "SDP","mlb","SEA","STL","TBR","TEX","TOR","WSN")

# Run loop to pull data for the years we care about (defined using year_range parameter)
for (years in year_range){
  for (team in team_list){
    
    # Access web-page
    link <- paste("http://www.baseball-reference.com/teams/",team,"/",years,
                  "-schedule-scores.shtml#team_schedule",sep="")
    
    # Read scraped data
    tbl <- readHTMLTable(link, stringsAsFactors = FALSE)
    tbl <- tbl[[1]]
    
    # Create variables
    dayofWeek <- str_split_fixed(tbl$Date, ", ", 2)
    date <- str_split_fixed(dayofWeek[,c(2)], " ", 2)
    dayofWeek <- dayofWeek[,c(1)]
    tbl <- tbl[,c(1,3:20)]
    
    # Merge into a table
    tbl[c("DayofWeek","Month","Day")] <- NA
    tbl$DayofWeek <- dayofWeek
    tbl$Month <- date[,c(1)]
    tbl$Day <- date[,c(2)]
    
    # Rename columns
    names(tbl) <- c('game_num', 'year', 'team', 
                'home', 'opp_code', 'win_loss', 
                'runs', 'runs_against', 'innings', 'win_loss_record', 
                'rank', 'games_behind', 
                'win_pitcher', 'loss_pitcher', 'save_pitcher', 
                'time', 'day_night', 'attendance', 'streak',
                'day_of_week', 'month', 'day')
    
    # Add year / date data
    tbl <- tbl %>%
      mutate(year = years)
    
    tbl[c("date")] <- NA
    tbl$date <- tolower(paste(tbl$year, tbl$month, tbl$day, sep=""))
    tbl <- tbl[,c(1,2,20:23,3:19)]

    # Bind into one table
    gamedata <- rbind(gamedata,tbl)
                 }
}

# Remove blank rows in the dataset
gamedata <- gamedata[gamedata$game_num !="Gm#", ]

# Convert data types for use in modeling
gamedata <- gamedata %>%
  mutate(game_num = as.numeric(game_num),
         year = as.numeric(year),
         day = as.numeric(day),
         date = as.Date(date, "%Y%b%d"),
         runs = as.numeric(runs),
         runs_against = as.numeric(runs_against),
         innings = as.numeric(innings),
         rank = as.numeric(rank),
         attendance = as.numeric(attendance)
         )

# Create home game indicator
gamedata <- gamedata %>%
  mutate(home = replace(home, home == '@', 'No'),
         home = replace(home, home == '', 'Yes'))

# Separate win-loss record
gamedata <- gamedata %>%
  mutate(wins   = as.numeric(str_split_fixed(gamedata$win_loss_record, '-', 2)[, 1]),
         losses = as.numeric(str_split_fixed(gamedata$win_loss_record, '-', 2)[, 2]),
         win_diff = wins - losses,
         win_pct  = wins / (wins + losses))

# Sort the data
gamedata <- gamedata %>%
  arrange(team, year, date)

# Check for NAs by column
gamedata %>% 
  apply(2, function(x) {sum(is.na(x))}) %>% 
  as.data.frame()

# Subset game data for merging
gamedata_subset <- gamedata %>%
  dplyr::select(-game_num, -day_of_week, -month, -day, -day_night, -time,
         -games_behind, -innings, -attendance, -win_loss_record)

# Isolate mlb data
mlb_data <- gamedata_subset %>% 
  filter(team == 'mlb') %>%
  dplyr::select(-team, -opp_code) %>%
  distinct(year, date, .keep_all = TRUE)

# Standardize column names
names(mlb_data)[3:ncol(mlb_data)] <- paste0('mlb_', names(mlb_data)[3:ncol(mlb_data)])

# Add mlb homespan streak
mlb_data$mlb_homespan <- sequence(rle(as.character(mlb_data$mlb_home))$lengths)
mlb_data <- mlb_data %>%
  mutate(mlb_homespan = replace(mlb_homespan, mlb_home == 'No', 0))

# Merge both mlb and opponent data with our master file
sales_master <- sales_master %>%
  left_join(mlb_data, by = c('year', 'date'))

```
 
# Preparing Data for Modeling

We filter our data to only include the seasons we care about (in this case, we chose to only include data from 2015-2016 to counter the effects of duration dependence).
```{r}
# Filter data to only include prior to years of data
tix <- sales_master %>% filter(date >= season_start) # 2015-2016 season start

# Refactor variables for modeling purposes
tix <- as.data.frame(lapply(tix, function (x) if (is.factor(x)) factor(x, ordered = F) else x))

```

Next, we split our datasets by ticket type (Single, Group, and Special Event) and group the data appropriately for our analysis.
```{r}
# Initalize loop
for(i in tix_type){
  # Create tibbles to house data
  assign(paste0("tix_cum_", i),tibble())
  assign(paste0("tix_", i),tibble())
  
  # Filter data
  assign(paste0("tix_", i), filter(tix, buyer_type_group_code == i))
  
  # Group variables appropriately
  assign(paste0("tix_cum_",i), group_by(get(paste0("tix_",i)), buyer_type_group_code,
             opp_code,
             month,
             day,
             night_day,
             mlb_homespan,
             day_diff,
             last_week,
             spc_event_cat
             ) %>%
      dplyr::summarize(ntix = n(), 
                       mean_price = mean(total_price)))
}  

```

We trim our dataset to only include the modeling features we're interested in using (defined by model_variables).
```{r}
# Select the features we want to use for both sets of data (NOTE: code was moved to beginning of file to enable users to select parameters upfront)
model_variables_SPCEVT <- c(model_variables, "spc_event_cat") # We need to include special event categories where applicable

# Filter datasets using these variables
for(i in tix_type){
  # We need to treat SPCEVT differently, so let's use an if() function
  if(i == "SPCEVT"){
    as.factor(get(paste0("tix_cum_", i))$month)
    assign(paste0("tix_cum_fil_", i), get(paste0("tix_cum_", i))[, model_variables_SPCEVT])
  } else {
    as.factor(get(paste0("tix_cum_", i))$month)
    assign(paste0("tix_cum_fil_", i), get(paste0("tix_cum_", i))[, model_variables])
  }
}

```

We automate the model.matrix and feature creation processes to save time.
```{r}
# Loop through each game type. This code works when you run it twice, so we've built in code to do this automatically and workaround an error we were seeing.
for(i in tix_type){
  
  # Use modex.matrix to convert factors into quantitative indicators
  tryCatch({assign(paste0("tix_cum_fil_", i), as.data.frame(model.matrix(~., get(paste0("tix_cum_fil_", i))))[,-1])}, error = function(e){})# NOTE: [,-1] simply drops the intercept column
  
  # Remove dashes (disrupt model processes)
  colnames(tix_cum_fil_SINGLE) <- gsub("-", "_", colnames(tix_cum_fil_SINGLE))
  colnames(tix_cum_fil_GROUP) <- gsub("-", "_", colnames(tix_cum_fil_GROUP))
  colnames(tix_cum_fil_SPCEVT) <- gsub("-", "_", colnames(tix_cum_fil_SPCEVT))
  
  # Create feature string for each model
  assign(paste0("feats", i), names(get(paste0("tix_cum_fil_", i))[,-c(1)]))
  assign(paste0("feats", i), paste(get(paste0("feats", i)), collapse = ' + '))
  assign(paste0("feats", i), as.formula(paste('ntix ~', "poly(log(-day_diff + 1), 2) + ", gsub("day_diff + ", "", get(paste0("feats", i))))))

}

```

Finally, we load-in our prediction template and perform the necessary data wrangling steps to prepare the raw format for modeling.
```{r}

# Read in Prediction Template (manually filled-out by user)
template <- read.csv("Prediction Template.csv")

# Rename variables
template <- template %>%
  rename(day = Day,
         date = Date,
         month = Month,
         opp = Opp,
         event_code = Event.Code,
         night_day = Day.Night,
         time = Time,
         spc_event_cat = Special_Event_Category,
         mlb_homespan = Homespan)

# Correct date
template <- template %>%
  mutate(date = mdy(date))

# Correct opp_code
template <- template %>% # ONLY needed when using Sales_Master source data file
  rename(opp_code = opp) %>% 
  mutate(opp_code = as.character(opp_code),
         opp_code = replace(opp_code, opp_code == 'CWS', 'CHW'),
         opp_code = replace(opp_code, opp_code == 'SD', 'SDP'),
         opp_code = replace(opp_code, opp_code %in% c('WAS', 'WSH'), 'WSN'))

# Correct day, month
template <- template %>% 
  mutate(date = as_date(date),
         day = wday(date, label = TRUE),
         month = month(date, label = TRUE),
         time = hm(time),
         night_day ='Day',
         night_day = replace(night_day, hour(time) >= 17, 'Night')) # After 5 PM


# Create dummy day_diff
day_diff_matrix <- matrix(, ncol = 2)
colnames(day_diff_matrix) <- c("event_code", "day_diff")

for(i in unique(template$event_code)){
  x_loop <- cbind(i, matrix(-150:0, nrow = 151, ncol = 1))
  colnames(x_loop) <- c("event_code", "day_diff")
  day_diff_matrix <- rbind(day_diff_matrix, x_loop)
}
template_filled <- left_join(as.data.frame(day_diff_matrix), template, c("event_code" = "event_code"))[-1,]
template_filled$day_diff <- as.numeric(as.character(template_filled$day_diff))

# Correct last_week
template_filled <- template_filled  %>%
  mutate(year = year(date),
         last_week = day_diff,
         last_week = replace(last_week, day_diff < -7, 'No'),
         ntix = 0
         )

# Re-factor for modeling purposes
template_filled <- as.data.frame(lapply(template_filled, function (x) if (is.factor(x)) factor(x, ordered = F) else x))

# Find the name of opponents from previous seasons
nec_opp <- as.vector(paste0("opp_code", unique(tix$opp_code)))

# Find the name of opponents from previous seasons
nec_spc_event <- as.vector(paste0("spc_event_cat", unique(tix$spc_event_cat)))

# Create prediction files
for(i in tix_type){
  # We need to treat SPCEVT differently, so let's use an if() function
  if(i == "SPCEVT"){
    if(nlevels(template_filled$spc_event_cat) == 1){ # If spc_event_cat is filled with NAs, we need to ignore
      template_filled_ <- template_filled[, model_variables_SPCEVT]
    } else {
      template_filled_ <- template_filled[, model_variables]
    }
  } else {
    template_filled_ <- template_filled[, model_variables]
}
  
# Use model matrix to get indicators
template_filled_i <- as.data.frame(model.matrix(~., template_filled_))[,-1]

# Remove dashes and spaces
colnames(template_filled_i) <- gsub("-", "_", colnames(template_filled_i))
colnames(template_filled_i) <- gsub(" ", "_", colnames(template_filled_i))
  
# Finally, it's possible that our team  won't play a particular team that they had played in the 2015-2016 seasons. We need to add dummy columns to correct this issue where applicable
missing_opp <- setdiff(nec_opp, colnames(template_filled_i)) # Find missing opponents
missing_spc_event <- setdiff(nec_spc_event, colnames(template_filled_i))
template_filled_i[missing_opp] <- 0 # Add zeroes to data frame
template_filled_i[missing_spc_event] <- 0
  
# Store data
assign(paste0("pred_template_", i), template_filled_i)
}


```

# Model Building

We chose to use a NBD regression to model our three different buyer_types as it is designed to work well with discrete, non-negative variable types. This model effectively captures heteregeneity by allowing each individual's lambda (their propensity to purchase tickets, modeling using a Poisson distribution) to vary according to the Gamma distribution. Additional rationale can be found in our final presentation deck.

This final output will save our projections in a .csv file and export several plots which can be used to estimate sales over time.
```{r}
# Load MASS package for NBD model (can mess with dplyr, so we're loading this one package at the end)
pacman::p_load(MASS)

# Initialize data frame to store results
for(i in tix_type){
  mod_name <- get(paste0("tix_cum_fil_", i))
  pred_name <- get(paste0("pred_template_", i))
  features <- get(paste0("feats", i))
    
  # Fit NBD regression
  nbd.fit <- glm.nb(features, data = mod_name)
  
  # Predict results in pred_template
  assign(paste0("pred", i), predict(nbd.fit, pred_name, type= "response"))
}

# Bind predictions to template
Prediction_Output <- cbind(subset(template_filled, select = -c(ntix)), predSINGLE, predGROUP, predSPCEVT)

# Clarify game date vs. actual date
Prediction_Output <- Prediction_Output %>%
  mutate(Sale_Date = Prediction_Output$day_diff + Prediction_Output$date) %>%
  rename(Game_Date = date)

# Save results to output file
write.csv(Prediction_Output, paste0("Prediction_Output_", Sys.Date(), ".csv"))

# Build graph for every game
for(game in unique(Prediction_Output$event_code)){
  tix_plot <- Prediction_Output %>%
    filter(game == event_code) %>%
    ggplot(aes(x = Sale_Date)) + 
      geom_smooth(aes(y = predSINGLE, color = "blue"), stat = "identity") + 
      geom_smooth(aes(y = predGROUP, color = "red"), stat = "identity") + 
      geom_smooth(aes(y = predSPCEVT, color = "black"), stat = "identity") + 
      scale_colour_manual(guide = 'legend', name = 'Legend', values = c('blue'='blue','red'='red', 'black'='black'), labels = c('Single','Group', 'Special Event')) +
    labs(y = "Ticket Sales") + ggtitle(game)
  
  # Save plots in image folder
  ggsave(paste0(img_dir, "prediction_", game, '.png'), 
     plot = tix_plot, width = 10, height = 7)
      
}

```
